---
title: "Homework 1- Exercise 2"
author: "Ashlyn Pernice"
date: "1/23/2020"
output: html_document
---
# Mtcars Dataset Exploration 

*This is exercise 2 of homework 1 for Data Science & Programming. In this R markdown file, I will be briefly exploring the mtcars dataset. This dataset has 11 variables for each type of car: miles per gallon, number of cylinders, displacement, gross horsepower, rear axle ratio, weight, 1/4 mile time, V/S, transmission type, number of forward gears, and number of carburetors. * 


*Here is a look at the structure of the dataset.* 
```{r structure of the data}
str(mtcars)







```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
*Here are the types of cars included in the dataset.*
```{r}
row.names(mtcars)

```

*Below is a quick summary for the mtcars dataset.*

```{r}

summary(mtcars) 


```

*Now let's look at some important information for the dataset.*


*Here are the cars with over 26 miles per gallon. This can help us distinguish the most fuel efficient vehicles* 

```{r}

mtcars[mtcars$mpg > 26,] 



```


